\documentclass[10pt]{article}
\begin{document}
 \paragraph{ INVESTIGATION ON POLLUTION AROUND MAKERERE UNNIVERSITY. }
\paragraph{by KAGAME STEVENLUC , Stdno: 216012220 ,Regno:16/U/5127/PS}
\paragraph{INTRODUCTION}

\paragraph{The area where this research was carried out covers kikoni student's residential places,Wandegeya city and Kagugube where most activities such as marketing,car repair annd transportion of people and things takes place.}\subparagraph{The research was carried out to find out how pollution can be reduced by picking out the main ways pollution is happening.}
\paragraph{FINDINGS}
\subparagraph{Firstly as a result of may old cars five years and plus to be momre specific being driven, there is too much air pollution due to the carbonic gases exposed in air.alsso the many cooking places and dusty murum roads air pollution is happening every day.}
\subparagraph{Secondly due to many small businessses especially shops and roadside food places that use polythene bags to pack food for students so many places have polythene bags poorly disposed off hence land pollution and as a result so many stagnant dirty waters havve formed because  water cannot freely be sucked up by the earth. }
\subparagraph{On interviewing one of the shop owners that was not using the polythene bags like any others he repliedand said"polythene takes 5 and moreyears to decompose,so we are killing the same eath that we want our kids to live in and the way to stop it is if the consumers refuse to be given the black beveras so they can be stopped from production". }
\paragraph{PROBLEMS ASSOCIATED WITH POLLUTION }
\subparagraph{because of air pollution many diseases such as lung cancer,heart attacks,asthma are so common in our country.land pollution slums and and less trees growing compared to what the earth is supposed to produce}
\paragraph{ALTERNATIVES} \subparagraph{Strong policies should be introduced and implemented for example cars that old(five years old) should be stopped from being driven,production of plythene bags should be banned and also industries that release or pollute the air should be closed if they cannot regulate the amount of smoke they expose to the air.}
\subparagraph{the above research was done by observaion mainly and a few interviews.}

\end{document}
